EGGs are adhesive!\\ An algebraic account of equality saturation

### 2025-09-08 jlamp/jlamp.tex
sez.4

\begin{rem}\label{rem:mprun}
	Let $(f,g)$ and $(h, k)$ be two morphisms $\mathcal{G}\rightrightarrows \mathcal{H}$ of $\hyp$ with $\mathcal{G}$ pruned and suppose that $f=h$. We can use the absence of isolated nodes in $\mathcal{G}$ to show that $g=k$ too. Let $v\in V_{\mathcal{G}}$, we have two cases:
	\begin{itemize}
		\item $v$ occurs in $s_{\mathcal{G}}(e)$ for some $e\in E_{\mathcal{G}}$. Let $1\leq i\leq \lgh_{V_{\mathcal{G}}}(s_{\mathcal{G}}(e))$ be such that $v=s_{\mathcal{G}}(e)_i$, then we have
		\[g(v)=g(s_{\mathcal{G}}(e)_i)=(g^\star(s_{\mathcal{G}}(e)))_i=s_{\mathcal{H}}(f(e))_i=s_{\mathcal{H}}(h(e))_i=(k^\star(s_{\mathcal{G}}(e)))_i=k(s_{\mathcal{G}}(e)_i)=k(v)\]
		\item $v$ occurs in $t_{\mathcal{H}}(e)$ for some $e\in E_{\mathcal{H}}$. Let $1\leq i\leq \lgh_{V_{\mathcal{H}}}(t_{\mathcal{G}}(e))$ be such that $v=t_{\mathcal{G}}(e)_i$, then we have
		\[g(v)=g(t_{\mathcal{G}}(e)_i)=(g^\star(t_{\mathcal{G}}(e)))_i=t_{\mathcal{H}}(f(e))_i=t_{\mathcal{H}}(h(e))_i=(k^\star(t_{\mathcal{G}}(e)))_i=k(t_{\mathcal{G}}(e)_i)=k(v)\]
	\end{itemize}
	In both cases $\hat{g}(v)=k(v)$ and so $\hat{g}= k$ as wanted.
\end{rem}

@@

\begin{rem} The functors $\pr$ and $\sp_P$ induce right adjoints to the inclusions $P_\mathcal{G}\colon \phyp_\mathcal{G} \to \hyp_{\mathcal{G}}$ and $S_{p, \mathcal{G}}\colon \pshyp_\mathcal{G}\to \phyp_{\mathcal{G}}$.
\end{rem}
We can easily realize $\lmo_{\mathcal{G}}$ and $\shyp_{\mathcal{G}}$ as comma categories.

@@

\begin{thm} Let $\mathcal{G}$ be an hypergraph, then %the following fact hold
%	\begin{enumerate}
%		\item an arrow $(f,g)$  if and only if is so in $\lmo$; \marginpar{ovvero?}
		%\item 
		$\lmo_{\mathcal{G}}$ is quasiadhesive and $\pshyp_{\mathcal{G}}$ is adhesive.
%	\end{enumerate}
\end{thm}

@@

\begin{rem}\label{rem:obv1}
By definition, there exist functors $a$ as in the diagrams below, where the horizontal arrows are full and faithful inclusions.
\[\xymatrix{\Eqlmo \ar[r]^-{M_{\mathsf{eq}}} \ar[d]_{O_{\mathsf{eq}}}& \EqHyp\ar[d]^{T} & \EqsHyp \ar[r]^-{S_{\mathsf{eq}}} \ar[d]_{R_{\mathsf{eq}}} & \EqHyp \ar[d]^{T} & \EqpsHyp \ar[r]^-{S_{p, \mathsf{eq}}} \ar[d]_{W_{\mathsf{eq}}} & \EqHyp\ar[d]^{T}\\ \lmo \ar[r]_{M} & \hyp & \shyp \ar[r]_{S} & \hyp  & \pshyp \ar[r]_-{S_p}& \hyp}\]

@@

			Notice that, if $\Sigma$ is algebraic, than such a function exists only if $\mathcal{H}$ is algebraic too. In that case the second diagram commute by default.
		\end{rem}
\end{minipage} \hfill 
\begin{minipage}[r]{.15\linewidth}
	\xymatrix{xy code}
	\end{minipage}

@@

Let $V_\Sigma\colon \EqHyps\to \EqHyp$ be the functor forgetting the labelling and $\pbc_\Sigma$ the class of morphisms in $\EqHyps$ whose image in $\EqHyp$ is in $\pbc$. From \Cref{prop:eqhyp_complete,cor:pbapp}, the second point of \Cref{thm:slice-functors,cor:eqade}, we can deduce the following.

\begin{prop}\label{prop:lim}Consider the forgetful functor $V_{\Sigma}\colon \EqHyps\to \EqHyp$. Then the following facts hold
	\begin{enumerate}
		\item $\EqHyps$ has all colimits and all connected limits, which are created by $V_{\Sigma}$;
		\item $\EqHyps$ is $\pbc_\Sigma$-adhesive.
	\end{enumerate}
\end{prop}

@@

We can now easily define term graphs with equivalence.

\begin{defi}Let $\Sigma$ be an algebraic signature.
	An object $(\mathcal{H}, l)$ of $\EqHyps$ is a \emph{term graph with equivalence} if $l\colon T(\mathcal{H})\to \mathcal{G}^\Sigma$ is a term graph. We denote by $\EqTG_{\Sigma}$ the full subcategory of $\EqHyps$ so defined and by $J_{\Sigma}$ the corresponding inclusion functor.
 \end{defi}

\noindent 
\begin{minipage}[l]{.72\linewidth}
	\begin{rem}\label{rem:obv}
		Let $T_\Sigma:  \EqHyps \to \hyp_{\Sigma}$ the functor sending an object of $\EqHyps$ to its underlying  labelled hypergraph.
		%
		%$T_\Sigma = T\circ V_\Sigma$.   
		Notice that, by definition, $(\mathcal{H}, l)$ is in $\EqTG_{\Sigma}$ amounts to say that $(T(\mathcal{H}), l)$ is in $\tg$. 
		Thus there exists a functor $S_\Sigma$ as in the diagram on the right.
		%Let $T_\Sigma$ be the functor sending $(\mathcal{H}, l)$ to $(T(\mathcal{H}), T(l))$.   Notice that, by definition, $(\mathcal{H}, l)$ is in $\EqTG_{\Sigma}$ if and only if $T(\mathcal{H})$ is in $\tg$. Thus there exists a functor $S_\Sigma$ as in the diagram on the right.
	\end{rem}
\end{minipage}
\hfill 
\begin{minipage}[r]{.23\linewidth}
	\xymatrix@R=15pt{\EqTG_{\Sigma} \ar[r]_{J_\Sigma}  \ar[d]_{S_\Sigma}& \EqHyps \ar[d]^{T_\Sigma} \\ \tg \ar[r]^{I_\Sigma}& \hyp_{\Sigma}}
\end{minipage}

@@

\begin{rem}\label{rem:map2}
	contenuto...
\end{rem}
\section{EGGs}
\label{eggs}
The previous section proved some adhesivity property for the categories $\EqHyp$ and $\EqTG_{\Sigma}$. We extend these results to
encompass equivalence classes which are closed under the target arrow, i.e.~under operator composition for term graphs, thus precisely capturing EGGs.

@@

Now let $(h,k)$ be another morphism $\mathcal{H}\to \sp(\mathcal{G})$ such that $(\id{E_{\mathcal{G}}}, \epsilon_{G})\circ S_p(h, k)=(f,g)$. This entails immediately that $h =f$ and so uniqueness follows from \Cref{rem:mprun}.	\qedhere 
	\end{enumerate}	
\end{proof}

@@

\trm*
\begin{proof}\label{proof:term}
	Let $F\colon \D\to \EqTG_{\Sigma}$ be the diagram of an equalizer, a binary product or of a pullback. By \Cref{prop:lim} we can consider a limiting cone $((\mathcal{L}, l), \{\pi_d\}_{d\in \D})$. By \Cref{rem:t} we know that $T_\Sigma$ preserves limits, thus by \Cref{rem:obv}  $(l, \{T_\Sigma(\pi_d)\}_{d\in \D})$ is limiting for $I_\Sigma\circ S_\Sigma$. Then by \Cref{prop:tlim} $l$ is a term graph. We conclude, again by \Cref{rem:obv} that $(\mathcal{L}, l)$ is in $\EqTG_{\Sigma}$ and the claim follows. 
\end{proof}

@@

	We conclude using \Cref{prop:push,rem:obv}.
\end{proof}

\subsection{Proofs for \Cref{eggs}}
\elim*
\begin{proof}\label{proof:elim}
	Let $F: \D \to \egg$ be a diagram, with $F(d) = (A_d, B_d, Q_d, s_d, t_d, q_d)$.  Let $(U_d, u_1^d, u_2^d)$ be a kernel pair for $q_d\circ s_d$.
	Now let $(A, B, Q, s, t, q)$, together with projections $(\pi_E^d, \pi_V^d, \pi_Q^d)_{d\in \D}$, be the limit of $I \circ F$. Suppose that $(U, u_1, u_2)$ is the kernel pair of $q^\star\circ s$ and let $(L, (l_i)_{i \in \cat I})$ be the limit of $K \circ I \circ F$. If we show that it lies in $\egg$ we are done.

>>>>

\begin{rem}\label{rem:mprun}
	Let $(f,g)$ and $(h, k)$ be two morphisms $\mathcal{G}\rightrightarrows \mathcal{H}$ of $\hyp$ with $\mathcal{G}$ pruned and suppose that $f=h$. We can use the absence of isolated nodes in $\mathcal{G}$ to show that $g=k$ too. Let $v\in V_{\mathcal{G}}$, we have two cases:

	\begin{itemize}
		\item $v$ occurs in $s_{\mathcal{G}}(e)$ for some $e\in E_{\mathcal{G}}$. Let $1\leq i\leq \lgh_{V_{\mathcal{G}}}(s_{\mathcal{G}}(e))$ be such that $v=s_{\mathcal{G}}(e)_i$, then we have
		\[g(v)=g(s_{\mathcal{G}}(e)_i)=(g^\star(s_{\mathcal{G}}(e)))_i=s_{\mathcal{H}}(f(e))_i=s_{\mathcal{H}}(h(e))_i=(k^\star(s_{\mathcal{G}}(e)))_i=k(s_{\mathcal{G}}(e)_i)=k(v)\]
		\item $v$ occurs in $t_{\mathcal{H}}(e)$ for some $e\in E_{\mathcal{H}}$. Let $1\leq i\leq \lgh_{V_{\mathcal{H}}}(t_{\mathcal{G}}(e))$ be such that $v=t_{\mathcal{G}}(e)_i$, then we have
		\[g(v)=g(t_{\mathcal{G}}(e)_i)=(g^\star(t_{\mathcal{G}}(e)))_i=t_{\mathcal{H}}(f(e))_i=t_{\mathcal{H}}(h(e))_i=(k^\star(t_{\mathcal{G}}(e)))_i=k(t_{\mathcal{G}}(e)_i)=k(v)\]
	\end{itemize}
	In both cases $\hat{g}(v)=k(v)$ and so $\hat{g}= k$ as wanted.
\end{rem}

@@

\begin{rem} The functors $\pr$ and $\sp_P$ induce right adjoints to the inclusions $P_\mathcal{G}\colon \phyp_\mathcal{G} \to \hyp_{\mathcal{G}}$ and $S_{p, \mathcal{G}}\colon \pshyp_\mathcal{G}\to \phyp_{\mathcal{G}}$.
\end{rem}
We can easily realize $\lmo_{\mathcal{G}}$, $\shyp_{\mathcal{G}}$ and $\pshyp_{\mathcal{G}}$ as comma categories.

@@

\begin{thm} Let $\mathcal{G}$ be an hypergraph. Then %the following fact hold
%	\begin{enumerate}
%		\item an arrow $(f,g)$  if and only if is so in $\lmo$; \marginpar{ovvero?}
		%\item 
		$\lmo_{\mathcal{G}}$ is quasiadhesive and $\pshyp_{\mathcal{G}}$ is adhesive.
%	\end{enumerate}
\end{thm}

@@

\begin{rem}\label{rem:obv1}
By definition, there exist functors $O_{\eq}$, $R_{\eq}$ and $W_{\eq}$ as in the diagrams below, where the horizontal arrows are full and faithful inclusions.
\[\xymatrix{\Eqlmo \ar[r]^-{M_{\mathsf{eq}}} \ar[d]_{O_{\mathsf{eq}}}& \EqHyp\ar[d]^{T} & \EqsHyp \ar[r]^-{S_{\mathsf{eq}}} \ar[d]_{R_{\mathsf{eq}}} & \EqHyp \ar[d]^{T} & \EqpsHyp \ar[r]^-{S_{p, \mathsf{eq}}} \ar[d]_{W_{\mathsf{eq}}} & \EqHyp\ar[d]^{T}\\ \lmo \ar[r]_{M} & \hyp & \shyp \ar[r]_{S} & \hyp  & \pshyp \ar[r]_-{S_p}& \hyp}\]

@@

			Notice that, if $\Sigma$ is algebraic, then such a function exists only if $\mathcal{H}$ is algebraic too. In that case, since the image of $\lg_{V_{\mathcal{H}}}$ is simply the singleton $\{1\}$, the second diagram commutes by default.
		\end{rem}
\end{minipage} \hfill 
\begin{minipage}[r]{.15\linewidth}
	\xymatrix@R=8pt{E_{\mathcal{H}} \ar[r]_{l} \ar[d]_{s_{\mathcal{H}}}& O_{\Sigma} \ar[d]^{\ari_\Sigma}\\ V^\star_{\mathcal{H}} \ar[r]^{\lgh_{V_{\mathcal{H}}}} & \mathbb{N}}
	\xymatrix@R=8pt{E_{\mathcal{H}} \ar[r]_{l} \ar[d]_{t_{\mathcal{H}}}& O_{\Sigma} \ar[d]^{\coar_\Sigma}\\ V^\star_{\mathcal{H}} \ar[r]^{\lgh_{V_{\mathcal{H}}}} & \mathbb{N}}
	\end{minipage}

@@

Let $V_\mathcal{G}\colon \EqHyps\to \EqHyp$ be the functor forgetting the labelling and $\pbc_\mathcal{G}$ the class of morphisms in $\EqHyps$ whose image in $\EqHyp$ is in $\pbc$. From \Cref{prop:eqhyp_complete,cor:pbapp}, the second point of \Cref{thm:slice-functors} and from \Cref{cor:eqade}, we can deduce the following.

\begin{prop}\label{prop:lim}Consider the forgetful functor $V_\mathcal{G}\colon \EqHyps\to \EqHyp$. Then the following facts hold
	\begin{enumerate}
		\item $\EqHyps$ has all colimits and all connected limits, which are created by $V_\mathcal{G}$;
		\item $\EqHyps$ is $\pbc_\mathcal{G}$-adhesive.
	\end{enumerate}
\end{prop}

@@

We can now easily define left-monogamous, pruned ans separated labelled hypergraphs with equivalence.

\begin{defi}Let$\mathcal{G}$ be an hypergraph and $(\mathcal{H},(f,g))$ labelled hypergraph with equivalence.  We say that $(\mathcal{H},(f,g))$ is a \emph{left-monogamous} (resp.~\emph{separated, pruned}) $\mathcal{G}$-hypergraph if $\mathcal{H}$ is left-monogamous (resp.~separated, pruned).

	We will denote by $\lmo_{\eq, \mathcal{G}}$, $\shyp_{\eq, \mathcal{G}}$, $\pshyp_{\eq, \mathcal{G}}$ the subcategories of $\hyp_{\eq, \mathcal{G}}$ given by left-monogamous, separated, pruned  and separated labelled hypergraphs with equivalence.
 \end{defi}

 Clearly we can realize $\lmo_{\eq, \mathcal{G}}$, $\shyp_{\eq, \mathcal{G}}$, $\pshyp_{\eq, \mathcal{G}}$ as comma categories.

 \begin{prop}
 	Let $M_{\eq}\colon \Eqlmo\to \EqHyp$ and $S_{\eq}\colon \EqsHyp \to \EqHyp$ be the inclusion functors. Let, moreover, $\Gamma_{R(\mathcal{G})}\colon 1\to \hyp$ be the constant functor in $R(\mathcal{G})$. Then
 	\begin{enumerate}
 		\item $\lmo_{\eq, \mathcal{G}}$ is equivalent to $\comma{M_\eq}{\Gamma_{R(\mathcal{G})}}$;
 		\item $\shyp_{\eq, \mathcal{G}}$ is equivalent to $\comma{S_\eq}{\Gamma_{R(\mathcal{G})}}$; 
 		\item $\pshyp_{\mathcal{G}}$ is equivalent to $\pshyp_{\eq}/R(\sp(\pr(\mathcal{G})))$. 
 	\end{enumerate}
 \end{prop}

\begin{defi}We define the following two classes of arrows:
	\begin{itemize}
		\item $\pbl_{\mathcal{G}}$ is the class of all arrows in $\lmo_{\eq, \mathcal{G}}$ sent by $M_{\eq, \mathcal{G}}$ to $\pbc_{\mathcal{G}}$;
		\item $\pbs$ is the class of all arrows in $\pshyp_{\eq, \mathcal{G}}$ sent by the inclusion  to $\pbc_{\mathcal{G}}$.
	\end{itemize}
\end{defi}

We can  now use \Cref{thm:slice-functors} to get the following.

\begin{cor}$\lmo_{\eq, \mathcal{G}}$ is $\pbl_{\mathcal{G}}$-adhesive and $\pshyp_{\eq, \mathcal{G}}$ is $\pbs_{\mathcal{G}}$-adhesive
\end{cor}

\begin{rem}When $\mathcal{G}$ is the hypergraph associated to an algebraic signature $\Sigma$, then left-monogamous labelled hypergraphs with equivalence are exactly the \emph{term graphs with equivalence} of \cite{uovadesive}.
\end{rem}
\iffalse 
\noindent 
\begin{minipage}[l]{.72\linewidth}
	\begin{rem}\label{rem:obv}
		Let $T_\Sigma:  \EqHyps \to \hyp_{\Sigma}$ the functor sending an object of $\EqHyps$ to its underlying  labelled hypergraph.
		%
		%$T_\Sigma = T\circ V_\Sigma$.   
		Notice that, by definition, $(\mathcal{H}, l)$ is in $\EqTG_{\Sigma}$ amounts to say that $(T(\mathcal{H}), l)$ is in $\tg$. 
		Thus there exists a functor $S_\Sigma$ as in the diagram on the right.
		%Let $T_\Sigma$ be the functor sending $(\mathcal{H}, l)$ to $(T(\mathcal{H}), T(l))$.   Notice that, by definition, $(\mathcal{H}, l)$ is in $\EqTG_{\Sigma}$ if and only if $T(\mathcal{H})$ is in $\tg$. Thus there exists a functor $S_\Sigma$ as in the diagram on the right.
	\end{rem}

	\[	\xymatrix@R=8pt@C=10pt{& \pshyp_\mathcal{G} \ar[dd]_(.7){W_\mathcal{G}}|\hole \ar@/_.2cm/@{_{(}->}[rr]_{S_{p,\mathcal{G}}} \ar@{_{(}->}[dl]_{I_\mathcal{G}} && \phyp_\mathcal{G} \ar[dd]^(.7){V_\mathcal{G}}|\hole \ar@/_.2cm/[ll]^{\sp_\mathcal{G}}\ar@/_.2cm/@{_{(}->}[dr]_(.35){P_\mathcal{G}}\\\shyp_\mathcal{G} \ar@{^{(}->}[rr]^(.35){S_\mathcal{G}} \ar[dd]_{R_\mathcal{G}}&& \lmo_\mathcal{G}  \ar@{^{(}->}[rr]^(.35){M_\mathcal{G}} \ar[dd]_(.25){O_\mathcal{G}}&& \hyp_\mathcal{G} \ar@/_.2cm/[ul]_{\pr_\mathcal{G}} \ar[dd]^{U_\mathcal{G}}\\& \pshyp \ar@/_.2cm/@{_{(}->}[rr]_(.35){S_p}|\hole \ar@{^{(}->}[dl]_{I} && \phyp \ar@/_.2cm/[ll]^(.35){\sp}|\hole\ar@/_.2cm/@{_{(}->}[dr]_(.3){P}\\\shyp \ar@{_{(}->}[rr]^{S} && \lmo  \ar@{_{(}->}[rr]^(.35){M}&& \hyp \ar@/_.2cm/[ul]_{\pr}}\]
\end{minipage}
\hfill 
\begin{minipage}[r]{.23\linewidth}
	\xymatrix@R=15pt{\EqTG_{\Sigma} \ar[r]_{J_\Sigma}  \ar[d]_{S_\Sigma}& \EqHyps \ar[d]^{T_\Sigma} \\ \tg \ar[r]^{I_\Sigma}& \hyp_{\Sigma}}
\end{minipage}

@@

\fi 
\section{EGGs}
\label{eggs}
The previous section proved some adhesivity property for the categories $\EqHyp$ and $\EqTG_{\Sigma}$. We extend these results to
encompass equivalence classes which are closed under the target arrow, i.e.~under operator composition for term graphs, thus precisely capturing EGGs.

@@

Now let $(h,k)$ be another morphism $\mathcal{H}\to \sp(\mathcal{G})$ such that $(\id{E_{\mathcal{G}}}, \epsilon_{G})\circ S_p(h, k)=(f,g)$. This entails immediately that $h =f$ and so uniqueness follows from \Cref{rem:mprun}.	\qedhere 
	\end{enumerate}

	Let $\mathcal{G}$ be an hypergraph. For every $e\in E_{\mathcal{G}}$, let $n_e=\lgh_{V_{\mathcal{G}}}(s_{\mathcal{G}}(e))$ and $m_e=\lgh_{V_{\mathcal{G}}}(t_{\mathcal{G}}(e))$. Given $1\leq i\leq n_e+m_e$,  we can define $\delta^e_i\colon \mto V_{\mathcal{G}}$ as
	\[\delta^e_i(0) =\begin{cases}
		s_{\mathcal{G}}(e)_i & \mbox{if } i\leq n_e\\
		t_{\mathcal{G}}(e)_{i-n_e} &  \mbox{otherwise}
	\end{cases}\]

	\smallskip 
	Hence $(\id{E_{\mathcal{G}}}, \epsilon_{G})$ is a morphism $P(\sp(\mathcal{G}))\to \mathcal{G}$. Now, let $(f,g)\colon P(\mathcal{H})\to \mathcal{G}$ be a  morphism of pruned hypergraphs with $\mathcal{H}$ separated. Given a node $v$ in $V_{\mathcal{H}}$ we know that there exists exactly one $e_v$ such that $v$ occurs in $s_{\mathcal{H}}(e_v)$ or in $t_{\mathcal{H}}(e_v)$. Moreover, $v$ occurs exactly once and not in both. Let $i_v$ be the index at which it appears. We define
	\[\hat{g}(v):=\begin{cases}
		\iota_{f(e_v)}(\iota^{f(e_v)}_{i_v}(0)) & \text{if } v \text{ occurs in } s_{\mathcal{H}}(e)\\
		\iota_{f(e_v)}(\iota^{f(e_v)}_{n_e + i_v}(0)) & \text{if } v \text{ occurs in } t_{\mathcal{H}}(e)\\
	\end{cases}\]
	Computing we get
	\begin{gather*}
		\hat{g}^\star(s_{\mathcal{H}}(e))= \hat{g}^\star(\prod_{i=1}^{n_e} s_{\mathcal{H}}(e)_i)=\prod_{i=1}^{n_e}(\hat{g}(s_{\mathcal{H}}(e)_i))=\prod_{i=1}^{n_e}\iota_{f(e)}( \iota^{f(e)}_i(0))=s_{\sp(\mathcal{G})}(f(e))\\
		\hat{g}^\star(t_{\mathcal{H}}(e))= \hat{g}^\star(\prod_{i=1}^{m_e} t_{\mathcal{H}}(e)_i)=\prod_{i=1}^{m_e}(\hat{g}(t_{\mathcal{H}}(e)_i))=\prod_{i=1}^{m_e}\iota_{f(e)}( \iota^{f(e)}_{n_e+i}(0))=\prod_{i=n_e + 1}^{n_e + m_e}\iota_{f(e)}( \iota^{f(e)}_{i}(0))=t_{\sp(\mathcal{G})}(f(e))
	\end{gather*}
	proving that $(f, \hat{g})\colon \mathcal{H}\to\sp( \mathcal{G})$ is a morphism of $\pshyp$. Notice that	
	\begin{align*}
		&\epsilon_\mathcal{G}(\hat{g}(v))=\begin{cases}
			\epsilon_\mathcal{G}(\iota_{f(e_v)}(\iota^{f(e_v)}_{i_v}(0))) & \text{if } v \text{ occurs in } s_{\mathcal{H}}(e_v)\\
			\epsilon_\mathcal{G}(\iota_{f(e_v)}(\iota^{f(e_v)}_{n_e + i_v}(0))) & \text{if }v \text{ occurs in } t_{\mathcal{H}}(e_v)
		\end{cases}=	\begin{cases}
		\delta^{f(e_v)}_{i_v}(0)& \text{if }v \text{ occurs in } s_{\mathcal{G}}(e)\\
		\delta^{f(e_v)}_{i_v}(0)& \text{if } v \text{ occurs in } t_{\mathcal{G}}(e)
		\end{cases}\\ =&
		\begin{cases}
			s_{\mathcal{G}}(f(e_v))_{i_v}& \text{if } v \text{ occurs in } s_{\mathcal{G}}(e)\\
			t_{\mathcal{G}}(f(e_v))_{i_v}& \text{if } v \text{ occurs in } t_{\mathcal{G}}(e)
		\end{cases}= \begin{cases}
		(g^\star(s_{\mathcal{H}}(e_v)))_{i_v}& \text{if } v \text{ occurs in } s_{\mathcal{G}}(e)\\
		(g^\star(t_{\mathcal{H}}(e_v)))_{i_v}& \text{if } v \text{ occurs in } t_{\mathcal{G}}(e)\\
		\end{cases}\\=&\begin{cases}
		g(s_{\mathcal{H}}(e_v)_{i_v})& \text{if } v \text{ occurs in } s_{\mathcal{G}}(e)\\
		g(t_{\mathcal{H}}(e_v)_{i_v})& \text{if } v \text{ occurs in } t_{\mathcal{G}}(e)\\
		\end{cases}=g(v)
	\end{align*}
and so $(\id{E_{\mathcal{G}}}, \epsilon_{G})\circ P(f, \hat{g})=(f,g)$.

	Now let $(h,k)$ be another morphism $\mathcal{H}\to \sp(\mathcal{G})$ such that $(\id{E_{\mathcal{G}}}, \epsilon_{G})\circ P(h, k)=(f,g)$. This entails immediately that $h =f$ and so uniqueness follows from \Cref{rem:mprun}.	
\end{proof}

@@

\iffalse 
\trm*
\begin{proof}\label{proof:term}
	Let $F\colon \D\to \EqTG_{\Sigma}$ be the diagram of an equalizer, a binary product or of a pullback. By \Cref{prop:lim} we can consider a limiting cone $((\mathcal{L}, l), \{\pi_d\}_{d\in \D})$. By \Cref{rem:t} we know that $T_\Sigma$ preserves limits, thus by \Cref{rem:obv}  $(l, \{T_\Sigma(\pi_d)\}_{d\in \D})$ is limiting for $I_\Sigma\circ S_\Sigma$. Then by \Cref{prop:tlim} $l$ is a term graph. We conclude, again by \Cref{rem:obv} that $(\mathcal{L}, l)$ is in $\EqTG_{\Sigma}$ and the claim follows. 
\end{proof}

@@

	We conclude using \Cref{prop:push,rem:obv}.
\end{proof}
\fi 
\subsection{Proofs for \Cref{eggs}}
\elim*
\begin{proof}\label{proof:elim}
	Let $F: \D \to \egg$ be a diagram, with $F(d) = (A_d, B_d, Q_d, s_d, t_d, q_d)$.  Let $(U_d, u_1^d, u_2^d)$ be a kernel pair for $q_d\circ s_d$.
	Now let $(A, B, Q, s, t, q)$, together with projections $(\pi_E^d, \pi_V^d, \pi_Q^d)_{d\in \D}$, be the limit of $I \circ F$. Suppose that $(U, u_1, u_2)$ is the kernel pair of $q^\star\circ s$ and let $(L, (l_i)_{i \in \cat I})$ be the limit of $K \circ I \circ F$. If we show that it lies in $\egg$ we are done.
